# Introduction {#sec:introduction}

<!-- An example of how to include text based on the language. The two chunks below shows how switching the toggle in the YAML header for french allows inclusion/rejection of a paragraph. -->

```{r para-chap01-1-en, eval=!fr(), results = 'asis'}
cat("Recreational catch estimation in British Columbia has historically been accomplished using a combination of creel surveys and logbook programs. Creel surveys involve overflights to determine effort and dockside fisher interviews. This data is supplemented by logbook programs where guides and lodges voluntarily submit catch data. However, there are substantial spatial and temporal gaps in the creel and logbook data, which targets the most heavily fished areas and months. A mandatory Internet Recreational Effort and Catch (iREC) survey was introduced in 2013 to resolve these gaps.

iREC is an online sport catch reporting system that randomly selects recreational licence holders to self-report kept and released fish by adipose clip status for a given month of the year. This survey covers all months and regions. License holders also report if they did not fish which is equally as important as reported catch. The values from iREC are calibrated against creel survey estimates and combined to fill in spatial and temporal gaps where there are no creel or logbook programs but fishing does occur. These data have been variably incorporated into the recreational catch since 2013 in most regions domestically, but this incorporation has not occurred in a standardized way. Furthermore, iREC has not be incorporated in catch estimates prior to 2013. The Pacific Salmon Treaty outlines a 2009-2015 base period for calculating calendar year exploitation rate (CYER). This base period currently combines incongruous data sources (a mix of yearly iREC-incorporated and yearly catch estimates without iREC) and creates a bias when comparing to current data (yearly iREC-incorporated catch estimates). 

Here, we present (1) a standardized method for combining quality-controlled creel and iREC data in years where both sources exist (2013-present) to generate the best recreational catch estimate by month and area, which is then rolled up to year and finescale fishery levels. (2) Next, in years where iREC is unavailable (before 2013), we model iREC-incorporated seasonal catch estimates by finescale fishery using the relationship between summertime creel estimates without iREC and seasonal iREC-incorporated catch estimates from 2013-2023. These seasonal estimates are then rolled up into yearly estimates. 



Welcome to report generation using `csasdown`. Included in this example document are many useful bits of information on how to write a reproducible report document using  the `csasdown` package, which is based on [Rmarkdown](https://rmarkdown.rstudio.com/) and [Bookdown](https://bookdown.org/). The information given in this example document should be used with all three `csasdown` document types: Research Document (`resdoc`), Science Response (`sr`), and Technical Report (`techreport`).")
```

```{r para-chap01-1-fr, eval=fr(), results = 'asis', needs_trans = FALSE}
cat("(This is where you would place the French translation of the paragraph. Once you do, set needs_trans to FALSE in the chunk header) Bienvenue dans la génération de rapports à l'aide de `csasdown`. Ce document d'exemple contient de nombreuses informations utiles sur la façon d'écrire un rapport reproductible à l'aide du paquetage `csasdown`, qui est basé sur [Rmarkdown] (https://rmarkdown.rstudio.com/) et [Bookdown] (https://bookdown.org/). Les informations données dans cet exemple doivent être utilisées avec les trois types de documents `csasdown` : Document de recherche (`resdoc`), Réponse scientifique (`sr`), et Rapport technique (`techreport`).

Traduit avec www.DeepL.com/Translator (version gratuite)")
```

```{r para-chap02-1-en, eval=!fr(), results = 'asis'}
cat("
If you get stuck on anything, read the `csasdown` [README](https://github.com/pbs-assess/csasdown/blob/master/README.md) carefully and all the [Wiki pages](https://github.com/pbs-assess/csasdown/wiki). There are many tips and tricks located in those pages. 

Inserting a hyperlink in Rmarkdown is easy, just look at the code for the paragraph above. It is located in **01_introduction.Rmd**

Include references in the **bib/refs.bib** file in the same format as the example that is already in the file. This is called *BiBLaTeX* format. Once you have added the reference, you can cite it using Rmarkdown in the following ways:

1. In parentheses: `[@edwards2013]` - renders as: [@edwards2013]
2. Inline: `@edwards2013` - renders as: @edwards2013
3. Without author: `[-@edwards2013]` - renders as: [-@edwards2013]

Some references: [@francis2011, @edwards2013, @swainbenoit2015].

Note that the year part of the citation is clickable and will take you directly to the reference in the References section.

Here is an example equation with the code used to generate it. Note that `csasdown` automatically numbers it on the right-hand side of the page. It does this consecutively throughout the document sections, but appendices are each numbered on their own, e.g. A.1, A.2, ... for Appendix A, and B.1, B.2, ... for Appendix B.")
```

```{r para-chap02-1-fr, eval = fr(), results = 'asis', needs_trans = TRUE}
<<para-chap02-1-en>>
```

````
\begin{equation}
  1 + 1
  \label{eq:test}
\end{equation}
````

\begin{equation}
  1 + 1
  \label{eq:test}
\end{equation}

A reference can be included anywhere in the text, to refer to a section or appendix. For the first appendix in this document, the code looks like this: `\@ref(app:first-appendix)`. Adding that code inline will create a clickable link in the output file: See Appendix \@ref(app:first-appendix).

The code inside the parentheses comes from the tag after the header for the section. For the appendix, the whole header line looks like:

`# THE FIRST APPENDIX {#app:first-appendix}`

Everything in the curly braces except for the hash sign is the tag you use to reference a section.

This section's header line looks like this:

`# Introduction {#sec:introduction}`

And can be referenced like this: `\@ref(sec:introduction)` which renders to this: Section \@ref(sec:introduction).

A reference to the equation above looks like this: `\@ref(eq:test)` and renders to this: Figure \@ref(eq:test). The labels for any type of reference (except for bibliography citations) are shown in Table \@ref(tab:ref-tab).

```{r ref-tab}
refs_tab <- tribble(
     ~`Reference type`,                    ~`Rmarkdown code`,
             "Section",        "`\\@ref(sec:section-label)`",
          "Subsection",  "`\\@ref(subsec:subsection-label)`",
            "Appendix",       "`\\@ref(app:appendix-label)`",
            "Equation",        "`\\@ref(eq:equation-label)`",
              "Figure",         "`\\@ref(fig:figure-label)`",
               "Table",          "`\\@ref(tab:table-label)`")

csasdown::csas_table(refs_tab,
  align = c("r", "r"),
  caption = ifelse(fr(),
                   "French goes here",
                   "Reference types and their Rmarkdown reference codes."))
```
