---
title: "Mark rate exploration"
author: "Norah Brown"
format: html
editor: visual
toc: true
toc-depth: 7
embed-resources: true
---

# Methods

-   We pulled raw recreational catch data from CREST database: data sources include creel, iREC, lodge and log-book data. Data is typically in number of marked and unmarked fish kept and released.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#load packages
library(tidyverse)
library(odbc)
library(lubridate)
library(ggnewscale)

#utils
"%notin%" <- Negate("%in%")

#Pull sport data from CREST
source("PullAllSport.R")
# PullAllSport(Start_year) set the calendar year to start querying from to the current year
rslt <- PullAllSport(2005)
quality_report <- rslt[[1]]
estimates <- rslt[[2]]
rm(rslt)
```

-   Filtered the creel data based on high quality creel which meet the following criteria in a given PFMA and month:
    -   At least 3 flights for each type of day (weekday or weekend)
    -   At least 25 interviews mid week OR at least 10% of interviews from mid-week
    -   At least 25 interviews on weekends OR at least 10% of interviews from weekend
    -   At least 15 day spread in flights
    -   At least 15 day spread in interviews

```{r Aligning creel and irec, echo=FALSE, message=FALSE, warning=FALSE}
Sport_filtered_south_irec_mr<-
  estimates |>
  as_tibble() |>
  filter(AREA %notin% c("Area 29 (In River)", "Campbell River", "Quinsam River", "CR-1", "CR-2", "CR-3", "CR-4", "QR-1", "QR-2", "QR-3", "QR-4", "Section PR-1", "Section PR-2", "Section PR-3")) |>
  mutate(AREA = case_when(
    str_detect(AREA, "Area 20") ~ "Area 20",
    #str_detect(AREA, "Area 23") ~ "Area 23",
    str_detect(AREA, "Area 19") ~ "Area 19",
    str_detect(AREA, "2E|2W") ~ "Area 2",
    AREA== "Area 29 (Marine)" ~ "Area 29",
    TRUE ~ as.character(AREA))) |>
  filter(SUB_TYPE == "LEGAL") |>
  mutate(REGION2 = case_when(AREA == "Area 2" ~ "NC", TRUE ~ REGION2)) |>
  mutate(MARKS_DESC = case_when(
         MARKS_DESC == "Not Adipose Checked" ~ "unchecked",
         MARKS_DESC == "Not Checked" ~ "unchecked",
         MARKS_DESC == "Not Applicable" ~ "unchecked",
         MARKS_DESC == "Not Adipose Marked" ~ "unmarked",
         MARKS_DESC == "Adipose Marked" ~ "marked")) |>
  mutate(SOURCE = case_when(
         SOURCE == "Creel" ~ "creel",
         SOURCE == "Historic" ~ "historic",
         SOURCE %in% c("Lodge Log","Lodge Manifest","Lodge Manifest - Log", "Lodge Estimate", "Log Estimate", "Lodge eLog") ~ "lodge_log",
         SOURCE == "iREC" ~ "irec_calibrated",
         TRUE ~ SOURCE )) |>
  group_by(YEAR, MONTH, AREA, REGION2, MANAGEMENT, SOURCE, MARKS_DESC, TYPE) |>
  summarise(VARIANCE=sum(VARIANCE), VAL=sum(ESTIMATE)) |> ungroup()
```

-   We calculated mark rate for each data source based on number of marked and unmarked fish encountered. We created a cut-off of data for n=100 fish in a given month. If the sample was less than that then there wasn't enough data to create a mark-rate estimate.

```{r expanding to all combinations, echo=FALSE, message=FALSE, warning=FALSE}
allobs3 <- tidyr::expand(Sport_filtered_south_irec_mr, nesting(AREA, REGION2, MANAGEMENT), YEAR, MONTH, MARKS_DESC, TYPE, SOURCE) %>%
                  filter(REGION2 %notin% c("NC", "CC", "NIT"))

#Add in commercial

Commercial_mr1<- read.csv(here::here("commercial_mark_rate.csv")) %>% as_tibble() %>% group_by(YEAR, AREA, MONTH) %>%  mutate(marked_prop_commercial=ADCLIP_OBS/ADCLIP_SAMPLE) %>% dplyr::select(YEAR, AREA, MONTH, marked_prop_commercial, ADCLIP_SAMPLE) %>% filter(AREA %notin% c("Area 1", "Area 101", "Area 142", "Area 2", "Area 8", "Area 3", "Area 4")) %>% filter(ADCLIP_SAMPLE>100)


```

-   Then we calculated an average of mark rate for the five year 2019-2023 period and one for the five year 2014-2018 period for each source.

-   After the averages were calculated, we combined data sources using the following rule:

    -   In months 5-9 use creel+ lodge if that data exists, otherwise use iREC

    -   In months outside of 5-9 use iREC

-   We included commercial troll data but this did not fill out the data frame any more than using only creel and iREC

```{r, echo=FALSE, message=FALSE, warning=FALSE}

Sport_mark_rate_only<- Sport_filtered_south_irec_mr  %>%
                  filter(REGION2 %notin% c("NC", "CC", "NIT")) %>% 
                  group_by(YEAR, MONTH, AREA, SOURCE, MARKS_DESC, TYPE) %>% summarise(sum=sum(VAL), sum_VARIANCE=sum(VARIANCE)) %>%
                  full_join(allobs3) %>%
                  pivot_wider(id_cols = c(YEAR, MONTH, AREA), names_from=c(MARKS_DESC, SOURCE), values_from = sum, values_fn = ~ sum(.x, na.rm = TRUE)) %>%
                 rowwise() %>%
                 mutate(marked_creel_plus = sum(marked_creel,marked_lodge_log, na.rm=TRUE),
                        unmarked_creel_plus = sum(unmarked_creel,unmarked_lodge_log, na.rm=TRUE),
                        marked_historic_plus = sum(marked_historic,marked_lodge_log, na.rm=TRUE), 
                        unmarked_historic_plus = sum(unmarked_historic,unmarked_lodge_log, na.rm=TRUE)) %>%
   mutate(marked_prop_creel = case_when(
     sum(marked_creel,unmarked_creel, na.rm =TRUE) > 100 ~ marked_creel/sum(marked_creel,unmarked_creel, na.rm =TRUE)),
          marked_prop_creel_plus = case_when(
           sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE) >100 ~ marked_creel_plus/sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE)), 
          marked_prop_lodge_log = case_when(
            sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)>100 ~ marked_lodge_log/sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)), 
           marked_prop_historic_plus = case_when(
             sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)>100 ~ marked_historic_plus/sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)), 
          marked_prop_irec_calibrated = case_when(
            sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)>100 ~ marked_irec_calibrated/sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)))%>% 
    mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  left_join(Commercial_mr1)
  
Sport_mark_rate_only_recent<- Sport_mark_rate_only %>% filter(YEAR %in% 2019:2023) %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, AREA) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))


Sport_mark_rate_only_past<- Sport_mark_rate_only %>% filter(YEAR %in% 2014:2018) %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, AREA) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))
                   
```

# Results

## Heat Map

### iREC & creel data combined 2019-current

-   Pink borders indicate the estimate includes data from iREC, without the border is creel-only information

```{r, echo=FALSE, message=FALSE, warning=FALSE}
library(paletteer)
library(ggthemes)

MR_post2019<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_catch_estimate, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "#1C00ff00"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Mark rate by PFMA",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate"))

MR_post2019
```

### iREC & creel data combined 2014-2018

```{r, echo=FALSE, message=FALSE, warning=FALSE}

MR_pre2019<-ggplot(data=Sport_mark_rate_only_past %>% filter(AREA %notin% c("Area 23"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_catch_estimate, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "#1C00ff00"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Mark rate by PFMA",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate"))

MR_pre2019
# library(patchwork)
# MR_post2019 + MR_pre2019 +  plot_layout(guides = "collect")
```

### Individual data sets

Datasets for 2019-2023 separated out by source.

```{r, echo=FALSE, message=FALSE, warning=FALSE}

library(patchwork)

PFMAMonth_irec_plot<-ggplot(data=Sport_mark_rate_only_recent%>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_irec_calibrated))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_irec_calibrated*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "iREC data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))


PFMAMonth_creel_plot<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_creel))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_creel*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Creel data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))

PFMAMonth_logbook_plot<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_lodge_log))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_lodge_log*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Logbook data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))

PFMAMonth_commercial_plot<-ggplot(data=Sport_mark_rate_only_recent%>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_commercial))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_commercial*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Commercial troll data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))


PFMAMonth_irec_plot
PFMAMonth_creel_plot 
PFMAMonth_logbook_plot 
PFMAMonth_commercial_plot

```

## Plots over time

Re-created these using the "best practices" combo of creel and irec

### Area 16

```{r, echo=FALSE, message=FALSE, warning=FALSE}

Sport_mark_rate_only_by_year<-Sport_mark_rate_only %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))


ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 16"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 16") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 17

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 17"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 17") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 18

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 18"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 18") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 19

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 19"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 19") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 20

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 20"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 20") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()

```

### Area 25

```{r, echo=FALSE, message=FALSE, warning=FALSE}
ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 25"), aes(y=marked_prop_catch_estimate, x=month(MONTH, label=TRUE) , col=AREA, group=AREA)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 25") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```
