---
title: "Mark rate exploration"
author: "Norah Brown"
date: today

editor: visual
execute: 
  warning: false

theme: litera
 
format:
  html:
    page-layout: full
    embed-resources: true
toc: true
toc-depth: 4
toc-location: left
---

# Methods

-   We pulled raw recreational catch data from CREST database: data sources include creel, iREC, lodge and log-book data. Data is typically in number of marked and unmarked fish kept and released.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#load packages
library(tidyverse)
library(odbc)
library(lubridate)
library(ggnewscale)

#utils
"%notin%" <- Negate("%in%")

#Pull sport data from CREST
source("PullAllSport.R")
# PullAllSport(Start_year) set the calendar year to start querying from to the current year
rslt <- PullAllSport(2005)
quality_report <- rslt[[1]]
estimates <- rslt[[2]]
rm(rslt)
```

-   Filtered the creel data based on high quality creel which meet the following criteria in a given PFMA and month:
    -   At least 3 flights for each type of day (weekday or weekend)
    -   At least 25 interviews mid week OR at least 10% of interviews from mid-week
    -   At least 25 interviews on weekends OR at least 10% of interviews from weekend
    -   At least 15 day spread in flights
    -   At least 15 day spread in interviews

```{r Aligning creel and irec, echo=FALSE, message=FALSE, warning=FALSE}
Sport_filtered_south_irec_mr<-
  estimates |>
  as_tibble() |>
  filter(AREA %notin% c("Area 29 (In River)", "Campbell River", "Quinsam River", "CR-1", "CR-2", "CR-3", "CR-4", "QR-1", "QR-2", "QR-3", "QR-4", "Section PR-1", "Section PR-2", "Section PR-3")) |>
  mutate(AREA = case_when(
    AREA== "Area 29 (Marine)" ~ "Area 29",
    AREA== "Area 19" & REGION2=="JDF" ~ "Area 19 (JDF)",
    AREA== "Area 19" & REGION2=="GSS" ~ "Area 19 (GS)",
    TRUE ~ as.character(AREA))) |>
  filter(SUB_TYPE == "LEGAL") |>
  mutate(REGION2 = case_when(AREA == "Area 2" ~ "NC", TRUE ~ REGION2)) |>
  mutate(MARKS_DESC = case_when(
         MARKS_DESC == "Not Adipose Checked" ~ "unchecked",
         MARKS_DESC == "Not Checked" ~ "unchecked",
         MARKS_DESC == "Not Applicable" ~ "unchecked",
         MARKS_DESC == "Not Adipose Marked" ~ "unmarked",
         MARKS_DESC == "Adipose Marked" ~ "marked")) |>
  mutate(SOURCE = case_when(
         SOURCE == "Creel" ~ "creel",
         SOURCE == "Historic" ~ "historic",
         SOURCE %in% c("Lodge Log","Lodge Manifest","Lodge Manifest - Log", "Lodge Estimate", "Log Estimate", "Lodge eLog") ~ "lodge_log",
         SOURCE == "iREC" ~ "irec_calibrated",
         TRUE ~ SOURCE )) |>
    mutate(AREA = case_when(
    SOURCE  != "irec_calibrated" & YEAR %in% c(2013:2019)  & grepl("Area 20", AREA) ~ "Area 20",
    SOURCE  != "irec_calibrated" & YEAR == 2020 & MONTH < 4 & grepl("Area 20", AREA) ~ "Area 20",
    SOURCE  != "irec_calibrated" & YEAR == 2013  & grepl("Area 23", AREA) ~ "Area 23",
    SOURCE  != "irec_calibrated" & YEAR == 2014  & MONTH < 4 & grepl("Area 23", AREA) ~ "Area 23",
    SOURCE  != "irec_calibrated" & YEAR == 2013 & grepl("2E|2W", AREA) ~ "Area 2",
    SOURCE  != "irec_calibrated" & YEAR == 2014 & MONTH < 4 & grepl("2E|2W", AREA)  ~ "Area 2",
    TRUE ~ as.character(AREA)
  )) |>
  group_by(YEAR, MONTH, AREA, REGION2, MANAGEMENT, SOURCE, MARKS_DESC, TYPE) |>
  summarise(VARIANCE=sum(VARIANCE), VAL=sum(ESTIMATE)) |> ungroup()
```

-   We calculated mark rate for each data source based on number of marked and unmarked fish encountered. We created a cut-off of data for n=100 fish in a given month. If the sample was less than that then there wasn't enough data to create a mark-rate estimate.

```{r expanding to all combinations, echo=FALSE, message=FALSE, warning=FALSE}
allobs3 <- tidyr::expand(Sport_filtered_south_irec_mr, nesting(AREA, REGION2, MANAGEMENT), YEAR, MONTH, MARKS_DESC, TYPE, SOURCE) %>%
                  filter(REGION2 %notin% c("NC", "CC", "NIT"))

#Add in commercial

Commercial_mr1<- read.csv(here::here("commercial_mark_rate.csv")) %>% as_tibble()  %>% filter(AREA %notin% c("Area 1", "Area 101", "Area 142", "Area 2", "Area 8", "Area 3", "Area 4")) %>% group_by(YEAR, AREA, MONTH) %>% summarise_if(is.numeric, sum, na.rm = TRUE) %>% mutate(marked_prop_commercial=ADCLIP_OBS/ADCLIP_SAMPLE) %>% filter(ADCLIP_SAMPLE>100)

Commercial_mr2<- read.csv(here::here("commercial_mark_rate.csv")) %>% as_tibble()  %>%    mutate(catch_region = case_when(
    AREA%in%c( "Area 125", "Area 126", "Area 127", "Area 121", "Area 123", "Area 124", "Area 21", "Area 24", "Area 23", "Area 23 (Barkley)", "Area 23 (Alberni Canal)", "Area 25", "Area 26", "Area 27") ~ "West Coast Vancouver Is Sport",
    AREA %in%c("Area 13", "Area 14", "Area 15", "Area 16")  ~ "Georgia Strait Sport Central",
    AREA %in%c("Area 17", "Area 18",  "Area 19 (GS)", "Area 28", "Area 29") ~ "Georgia Strait Sport South",
    AREA %in% c("Area 11", "Area 111", "Area 12")  ~ "Johnstone Strait Sport South",
    AREA %in% c("Area 10", "Area 106", "Area 110", "Area 6", "Area 7", "Area 8", "Area 9", "Area 130", "Area 108", "Area 109", "Area 107") ~ "Central Sport",
    AREA %in% c("Area 2","Area 1", "Area 101", "Area 102",  "Area 142", "Area 2E", "Area 2W", "Area 103", "Area 104", "Area 105", "Area 3", "Area 4", "Area 5") ~ "Northern Sport",
    AREA %in% c( "Area 19 (JDF)", "Area 20", "Area 20 (East)", "Area 20 (West)")   ~ "Juan de Fuca Sport")) %>% 
filter(AREA %notin% c("Area 1", "Area 101", "Area 142", "Area 2", "Area 8", "Area 3", "Area 4")) %>% group_by(YEAR, catch_region, MONTH) %>% summarise_if(is.numeric, sum, na.rm = TRUE) %>% mutate(marked_prop_commercial=ADCLIP_OBS/ADCLIP_SAMPLE) %>% filter(ADCLIP_SAMPLE>100)


```

-   Then we calculated an average of mark rate for the five year 2019-2023 period and one for the five year 2014-2018 period for each source.

-   After the averages were calculated, we combined data sources using the following rule:

    -   In months 5-9 use creel+ lodge if that data exists, otherwise use iREC

    -   In months outside of 5-9 use iREC

-   We included commercial troll data but this did not fill out the data frame any more than using only creel and iREC

```{r, echo=FALSE, message=FALSE, warning=FALSE}

Sport_mark_rate_only<- Sport_filtered_south_irec_mr  %>%
                  filter(REGION2 %notin% c("NC", "CC", "NIT")) %>% 
                  group_by(YEAR, MONTH, AREA, SOURCE, MARKS_DESC, TYPE) %>% summarise(sum=sum(VAL), sum_VARIANCE=sum(VARIANCE)) %>%
                  full_join(allobs3) %>%
                  pivot_wider(id_cols = c(YEAR, MONTH, AREA), names_from=c(MARKS_DESC, SOURCE), values_from = sum, values_fn = ~ sum(.x, na.rm = TRUE)) %>%
                 rowwise() %>%
                 mutate(marked_creel_plus = sum(marked_creel,marked_lodge_log, na.rm=TRUE),
                        unmarked_creel_plus = sum(unmarked_creel,unmarked_lodge_log, na.rm=TRUE),
                        marked_historic_plus = sum(marked_historic,marked_lodge_log, na.rm=TRUE), 
                        unmarked_historic_plus = sum(unmarked_historic,unmarked_lodge_log, na.rm=TRUE)) %>%
   mutate(marked_prop_creel = case_when(
     sum(marked_creel,unmarked_creel, na.rm =TRUE) > 100 ~ marked_creel/sum(marked_creel,unmarked_creel, na.rm =TRUE)),
          marked_prop_creel_plus = case_when(
           sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE) >100 ~ marked_creel_plus/sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE)), 
          marked_prop_lodge_log = case_when(
            sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)>100 ~ marked_lodge_log/sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)), 
           marked_prop_historic_plus = case_when(
             sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)>100 ~ marked_historic_plus/sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)), 
          marked_prop_irec_calibrated = case_when(
            sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)>100 ~ marked_irec_calibrated/sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)))%>% 
    mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  left_join(Commercial_mr1)

#By catch region
Sport_mark_rate_only_catch<- Sport_filtered_south_irec_mr  %>%
                  filter(REGION2 %notin% c("NC", "CC", "NIT")) %>% 
                  group_by(YEAR, MONTH, AREA, SOURCE, MARKS_DESC, TYPE) %>% summarise(sum=sum(VAL), sum_VARIANCE=sum(VARIANCE)) %>%
                  full_join(allobs3) %>%
      mutate(catch_region = case_when(
       AREA%in%c( "Area 125", "Area 126", "Area 127", "Area 121", "Area 123", "Area 124", "Area 21", "Area 24", "Area 23", "Area 23 (Barkley)", "Area 23 (Alberni Canal)", "Area 25", "Area 26", "Area 27") ~ "West Coast Vancouver Is Sport",
       AREA %in%c("Area 13", "Area 14", "Area 15", "Area 16")  ~ "Georgia Strait Sport Central",
       AREA %in%c("Area 17", "Area 18",  "Area 19 (GS)", "Area 28", "Area 29") ~ "Georgia Strait Sport South",
       AREA %in% c("Area 11", "Area 111", "Area 12")  ~ "Johnstone Strait Sport South",
       AREA %in% c("Area 10", "Area 106", "Area 110", "Area 6", "Area 7", "Area 8", "Area 9", "Area 130", "Area 108", "Area 109", "Area 107") ~ "Central Sport",
       AREA %in% c("Area 2","Area 1", "Area 101", "Area 102",  "Area 142", "Area 2E", "Area 2W", "Area 103", "Area 104", "Area 105", "Area 3", "Area 4", "Area    5") ~ "Northern Sport",
    AREA %in% c( "Area 19 (JDF)", "Area 20", "Area 20 (East)", "Area 20 (West)")   ~ "Juan de Fuca Sport")) %>% 

                  pivot_wider(id_cols = c(YEAR, MONTH, catch_region), names_from=c(MARKS_DESC, SOURCE), values_from = sum, values_fn = ~ sum(.x, na.rm = TRUE)) %>%
                 rowwise() %>%
                 mutate(marked_creel_plus = sum(marked_creel,marked_lodge_log, na.rm=TRUE),
                        unmarked_creel_plus = sum(unmarked_creel,unmarked_lodge_log, na.rm=TRUE),
                        marked_historic_plus = sum(marked_historic,marked_lodge_log, na.rm=TRUE), 
                        unmarked_historic_plus = sum(unmarked_historic,unmarked_lodge_log, na.rm=TRUE)) %>%
   mutate(marked_prop_creel = case_when(
     sum(marked_creel,unmarked_creel, na.rm =TRUE) > 100 ~ marked_creel/sum(marked_creel,unmarked_creel, na.rm =TRUE)),
          marked_prop_creel_plus = case_when(
           sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE) >100 ~ marked_creel_plus/sum(marked_creel_plus,unmarked_creel_plus, na.rm =TRUE)), 
          marked_prop_lodge_log = case_when(
            sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)>100 ~ marked_lodge_log/sum(marked_lodge_log,unmarked_lodge_log, na.rm =TRUE)), 
           marked_prop_historic_plus = case_when(
             sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)>100 ~ marked_historic_plus/sum(marked_historic_plus,unmarked_historic_plus, na.rm =TRUE)), 
          marked_prop_irec_calibrated = case_when(
            sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)>100 ~ marked_irec_calibrated/sum(marked_irec_calibrated,unmarked_irec_calibrated, na.rm =TRUE)))%>% 
    mutate_all(~ifelse(is.nan(.), NA, .)) %>%
  left_join(Commercial_mr2)


Sport_mark_rate_only$AREA<-factor(Sport_mark_rate_only$AREA, levels = c("Area 10", "Area 11", "Area 111", "Area 12", "Area 13", "Area 14", "Area 15", "Area 16", "Area 17", "Area 18", "Area 19 (GS)", "Area 19 (JDF)", "Area 20", "Area 20 (East)", "Area 20 (West)", "Area 121", "Area 123", "Area 124", "Area 21", "Area 23 (Alberni Canal)", "Area 23 (Barkley)", "Area 23","Area 24", "Area 125", "Area 126", "Area 127", "Area 25", "Area 26", "Area 27", "Area 28", "Area 29"))


  
Sport_mark_rate_only_recent<- Sport_mark_rate_only %>% filter(YEAR %in% 2019:2023) %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, AREA) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))

Sport_mark_rate_only_recent$marked_prop_source<-factor(Sport_mark_rate_only_recent$marked_prop_source, levels = c("calibrated iREC","creel plus logbook","commercial", "historic plus", "no source"))


Sport_mark_rate_only_recent_catch<- Sport_mark_rate_only_catch %>% filter(YEAR %in% 2019:2023) %>% dplyr::select(YEAR, MONTH, catch_region, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, catch_region) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))



Sport_mark_rate_only_past<- Sport_mark_rate_only %>% filter(YEAR %in% 2013:2018) %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, AREA) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))

Sport_mark_rate_only_past$marked_prop_source<-factor(Sport_mark_rate_only_past$marked_prop_source, levels = c("calibrated iREC","creel plus logbook","commercial", "historic plus", "no source"))

Sport_mark_rate_only_past_catch<- Sport_mark_rate_only_catch %>% filter(YEAR %in% 2013:2018) %>% dplyr::select(YEAR, MONTH, catch_region, marked_prop_lodge_log,marked_prop_creel, marked_prop_creel_plus,  marked_prop_historic_plus, marked_prop_irec_calibrated, marked_prop_commercial ) %>% group_by(MONTH, catch_region) %>%  summarise_if(is.numeric, mean, na.rm = TRUE) %>%  mutate(marked_prop_catch_estimate = case_when(
                   MONTH %in% c(5:9) & (is.na(marked_prop_creel) | marked_prop_creel %in% c(0,1)) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   MONTH %in% c(1:4,10:12) & !is.na(marked_prop_irec_calibrated) & marked_prop_irec_calibrated %notin% c(0,1) ~ as.numeric(marked_prop_irec_calibrated),
                   (marked_prop_irec_calibrated %in% c(0,1)| is.na(marked_prop_irec_calibrated)) ~ as.numeric(marked_prop_commercial),
                   TRUE ~ as.numeric(marked_prop_creel_plus))) %>% 
  mutate(marked_prop_source = case_when(
                   marked_prop_catch_estimate == marked_prop_irec_calibrated ~ "calibrated iREC",
                   marked_prop_catch_estimate == marked_prop_historic_plus ~ "historic plus",
                   marked_prop_catch_estimate == marked_prop_creel_plus ~ "creel plus logbook", 
                   marked_prop_catch_estimate == marked_prop_commercial ~ "commercial", 
                   TRUE ~ "no source"))
                   
```

# Results

## Heat Map

### iREC & creel data combined 2019-current by catch region

-   Pink borders indicate the estimate includes data from iREC, without the border is creel-only information

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-heatmap-current-catch-region
#| fig-cap: "Mark rate heatmap by management area and month. Mark rate is an average of mark rates from 2019-2023."
#| fig-alt: "Heatmap for mark rate in different catch regions organized by month of the year."
#| fig-width: 10
#| fig-height: 8

library(paletteer)
library(ggthemes)

MR_post2019_catch<-ggplot(data=Sport_mark_rate_only_recent_catch %>% filter(catch_region %notin% c("Central Sport"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(catch_region), fill = marked_prop_catch_estimate*100, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "#1C00ff00"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,100))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Average mark rate by catch region 2019-2023",
       x = "Month", y = "Catch Region") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate %"))

MR_post2019_catch
```

### iREC & creel data combined 2019-current

-   Pink borders indicate the estimate includes data from iREC, without the border is creel-only information

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-heatmap-current
#| fig-cap: "Mark rate heatmap by management area and month. Mark rate is an average of mark rates from 2019-2023."
#| fig-alt: "Heatmap for mark rate in different PFMAs organized by month of the year."
#| fig-width: 10
#| fig-height: 8

library(paletteer)
library(ggthemes)

MR_post2019<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_catch_estimate*100, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "pink4"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,100))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Average mark rate by PFMA 2019-2023",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate %"))

MR_post2019

#MR_pre2019_nl<-MR_pre2019 + theme(legend.position = "none")
#MR_pre2019_nl + MR_post2019+ plot_layout(guides = "collect")
#MR_post2019_catch
#MR_pre2019_catch + MR_post2019_catch+ plot_layout(guides = "collect")
```

### iREC & creel data combined 2013-2018

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-heatmap-pre2019
#| fig-cap: "Mark rate heatmap by management area and month. Mark rate is an average of mark rates from 2013-2018."
#| fig-alt: "Heatmap for mark rate in different PFMAs organized by month of the year.Using data from 2013-2018. "
#| fig-width: 10
#| fig-height: 8


MR_pre2019<-ggplot(data=Sport_mark_rate_only_past %>% filter(AREA %notin% c("Area 23"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_catch_estimate*100, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "pink4"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,100))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Average mark rate by PFMA 2013-2018",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate %"))

MR_pre2019
# library(patchwork)
# MR_post2019 + MR_pre2019 +  plot_layout(guides = "collect")
```

### iREC & creel data combined 2013-2018 Catch region

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-heatmap-pre2019-catch-region
#| fig-cap: "Mark rate heatmap by management area and month. Mark rate is an average of mark rates from 2013-2018."
#| fig-alt: "Heatmap for mark rate in different PFMAs organized by month of the year.Using data from 2013-2018. "
#| fig-width: 10
#| fig-height: 8


MR_pre2019_catch<-ggplot(data=Sport_mark_rate_only_past_catch %>% filter(catch_region %notin% c("Central Sport"), marked_prop_source %notin% c("no source")), aes(x=month(MONTH, label=TRUE), y=as.factor(catch_region), fill = marked_prop_catch_estimate*100, col=marked_prop_source))+
  geom_tile(linewidth=1) +
  scale_colour_manual(values = c("pink", "#1C00ff00", "#1C00ff00"))+
  geom_text(aes(label=round(marked_prop_catch_estimate*100, 0)), col="black")+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,100))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Average mark rate by catch region 2013-2018",
       x = "Month", y = "Catch Region") +
  theme_bw() + theme_minimal()+ guides(colour = guide_legend("Data source"), 
                                       fill = guide_colourbar("Mark rate %"))

MR_pre2019_catch
# library(patchwork)
# MR_post2019 + MR_pre2019 +  plot_layout(guides = "collect")
```

### Individual data sets

Datasets for 2019-2023 separated out by source.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label: fig-source
#| fig-cap: "Mark rate heatmap by management area and month. Mark rate is an average of mark rates from 2019-2023.Mark rate is separated by data source."
#| fig-subcap:
#|   - "iREC data only"
#|   - "creel data only"
#|   - "logbook data only"
#|   - "troll data only"
#| layout-ncol: 2
#| column: page


library(patchwork)

PFMAMonth_irec_plot<-ggplot(data=Sport_mark_rate_only_recent%>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_irec_calibrated))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_irec_calibrated*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "iREC data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))


PFMAMonth_creel_plot<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_creel))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_creel*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Creel data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))

PFMAMonth_logbook_plot<-ggplot(data=Sport_mark_rate_only_recent %>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_lodge_log))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_lodge_log*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Logbook data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))

PFMAMonth_commercial_plot<-ggplot(data=Sport_mark_rate_only_recent%>% filter(AREA %notin% c("Area 23")), aes(x=month(MONTH, label=TRUE), y=as.factor(AREA), fill = marked_prop_commercial))+
  geom_tile(colour = "white") +
  geom_text(aes(label=round(marked_prop_commercial*100, 0)))+
  scale_fill_paletteer_c("ggthemes::Blue-Teal", direction=1, na.value="#1C00ff00", limits=c(0,1))+
   scale_y_discrete(limits=rev)+
  scale_x_discrete(position = "top")+
  labs(title = "Commercial troll data only",
       x = "Month", y = "PFMA") +
  theme_bw() + theme_minimal()+ guides(fill = guide_colourbar("Mark rate"))


PFMAMonth_irec_plot
PFMAMonth_creel_plot 
PFMAMonth_logbook_plot 
PFMAMonth_commercial_plot

```

## Plots over time

Re-created these using the "best practices" combo of creel and irec

### Georgia Strait Central 

```{r, echo=FALSE, message=FALSE, warning=FALSE}

resize <- function(g, fig_width=NA, fig_height=NA) {
  g_deparsed <- paste0(deparse(function() g), collapse = '')
  sub_chunk <- paste0("`","``{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=", fig_height, ", fig.width=", fig_width, ", warning=FALSE, echo=FALSE}","\n(", g_deparsed, ")()","\n`","``")
  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}


library(patchwork)

Sport_mark_rate_only_by_year_catch<-Sport_mark_rate_only_catch %>% filter(YEAR >2013) %>% dplyr::select(YEAR, MONTH, catch_region, marked_prop_lodge_log, marked_prop_creel, marked_prop_irec_calibrated, marked_prop_commercial ) %>%  pivot_longer(cols = contains("marked"), names_to = "Source", values_to = "mark_rate")


Sport_mark_rate_only_by_year_av_past_catch<-Sport_mark_rate_only_by_year_catch %>% filter(YEAR %in% c(2013:2018)) %>% group_by(MONTH, catch_region, Source) %>% summarise(across(where(is.numeric), list(mean=mean, sd=sd), na.rm=TRUE))

Sport_mark_rate_only_by_year_av_recent_catch<-Sport_mark_rate_only_by_year_catch %>% filter(YEAR %in% c(2019:2023)) %>% group_by(MONTH, catch_region, Source) %>% summarise(across(where(is.numeric), list(mean=mean, sd=sd), na.rm=TRUE))


p1<-ggplot(Sport_mark_rate_only_by_year_av_past_catch %>% filter(catch_region=="Georgia Strait Sport Central"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent_catch %>% filter(catch_region=="Georgia Strait Sport Central"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Georgia Strait Sport Central')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year_catch %>% filter(catch_region=="Georgia Strait Sport Central"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Georgia Strait Sport Central") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Georgia Strait South

```{r, echo=FALSE, message=FALSE, warning=FALSE}


p1<-ggplot(Sport_mark_rate_only_by_year_av_past_catch %>% filter(catch_region=="Georgia Strait Sport South"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent_catch %>% filter(catch_region=="Georgia Strait Sport South"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Georgia Strait Sport South')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year_catch %>% filter(catch_region=="Georgia Strait Sport South"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Georgia Strait Sport South") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Johnstone Strait South

```{r, echo=FALSE, message=FALSE, warning=FALSE}


p1<-ggplot(Sport_mark_rate_only_by_year_av_past_catch %>% filter(catch_region=="Johnstone Strait Sport South"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent_catch %>% filter(catch_region=="Johnstone Strait Sport South"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Johnstone Strait Sport South')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year_catch %>% filter(catch_region=="Johnstone Strait Sport South"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Johnstone Strait Sport South") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Juan de Fuca Sport

```{r, echo=FALSE, message=FALSE, warning=FALSE}


p1<-ggplot(Sport_mark_rate_only_by_year_av_past_catch %>% filter(catch_region=="Juan de Fuca Sport"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent_catch %>% filter(catch_region=="Juan de Fuca Sport"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Juan de Fuca Sport')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year_catch %>% filter(catch_region=="Juan de Fuca Sport"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Juan de Fuca Sport") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### West Coast Vancouver Is Sport

```{r, echo=FALSE, message=FALSE, warning=FALSE}


p1<-ggplot(Sport_mark_rate_only_by_year_av_past_catch %>% filter(catch_region=="West Coast Vancouver Is Sport"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent_catch %>% filter(catch_region=="West Coast Vancouver Is Sport"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'West Coast Vancouver Is Sport')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year_catch %>% filter(catch_region=="West Coast Vancouver Is Sport"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("West Coast Vancouver Is Sport") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 16

```{r, echo=FALSE, message=FALSE, warning=FALSE}

resize <- function(g, fig_width=NA, fig_height=NA) {
  g_deparsed <- paste0(deparse(function() g), collapse = '')
  sub_chunk <- paste0("`","``{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=", fig_height, ", fig.width=", fig_width, ", warning=FALSE, echo=FALSE}","\n(", g_deparsed, ")()","\n`","``")
  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}


library(patchwork)
Sport_mark_rate_only_by_year<-Sport_mark_rate_only %>% filter(YEAR >2013) %>% dplyr::select(YEAR, MONTH, AREA, marked_prop_lodge_log, marked_prop_creel, marked_prop_irec_calibrated, marked_prop_commercial ) %>%  pivot_longer(cols = contains("marked"), names_to = "Source", values_to = "mark_rate")


Sport_mark_rate_only_by_year_av_past<-Sport_mark_rate_only_by_year %>% filter(YEAR %in% c(2013:2018)) %>% group_by(MONTH, AREA, Source) %>% summarise(across(where(is.numeric), list(mean=mean, sd=sd), na.rm=TRUE))

Sport_mark_rate_only_by_year_av_recent<-Sport_mark_rate_only_by_year %>% filter(YEAR %in% c(2019:2023)) %>% group_by(MONTH, AREA, Source) %>% summarise(across(where(is.numeric), list(mean=mean, sd=sd), na.rm=TRUE))


p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 16"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 16"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()+ ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 16')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 16"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 16") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 17

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 17"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 17"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 17')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 17"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 17") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 18

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 18"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 18"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<- p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 18')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 18"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source))  +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 18") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 19 GS

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 19 (GS)"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 19 (GS)"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 19 (GS)')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 19 (GS)"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source))  +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 19 (GS)") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```

### Area 19 JDF

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 19 (JDF)"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 19 (JDF)"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 19 (JDF)')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 19 (JDF)"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source))  +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 19 (JDF)") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()

```

### Area 20

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 20"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 20"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<-p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 20')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 20"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source))  +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 20") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()

```

### Area 25

```{r, echo=FALSE, message=FALSE, warning=FALSE}

p1<-ggplot(Sport_mark_rate_only_by_year_av_past %>% filter(AREA=="Area 25"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2013:2018") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)


p2<-ggplot(Sport_mark_rate_only_by_year_av_recent %>% filter(AREA=="Area 25"), aes(y=mark_rate_mean, x=month(MONTH, label=TRUE) , col=Source, group=Source)) +
  geom_point() +  geom_errorbar(aes(ymin=mark_rate_mean-mark_rate_sd, ymax=mark_rate_mean+mark_rate_sd), width=.1) + geom_line() + ggtitle("2019:2023") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw() + ylim(0,1)

p<- p1 + p2 + plot_layout(guides = "collect") + plot_annotation(
  title = 'Area 25')

p

# cat("\n\n")
# resize(p, 7, 4)
# cat("\n\n")

ggplot(Sport_mark_rate_only_by_year %>% filter(AREA=="Area 25"), aes(y=mark_rate, x=month(MONTH, label=TRUE) , col=Source, group=Source))  +
  geom_point() + geom_line()+  facet_wrap(~YEAR) + ggtitle("Area 25") +scale_x_discrete(guide = guide_axis(angle = 90)) + 
  xlab("Month") + ylab("Proportion marked")+ theme_bw()
```
