---
title: "Modelling_plots"
author: "Norah Brown"
date: today

editor: visual
execute: 
  warning: false

theme: litera
 
format:
  html:
    page-layout: full
    embed-resources: true
    code-fold: true
    code-summary: "Show the code"
toc: true
toc-depth: 4
toc-location: left
---

```{r Loading data, message=FALSE, warning=FALSE, results='hide', echo=FALSE}
#load packages
library(tidyverse)
library(odbc)
library(lubridate)
library(ggnewscale)
library(patchwork)
library(DHARMa)
library(lme4)
library(bbmle)
library(SuppDists)
library(MuMIn)
library(glmmTMB)

#utils
"%notin%" <- Negate("%in%")

col1 = "#d8e1cf"
col2 = "#438484"
col3 = "lightblue"
col4 = "lightblue4"
col5 = "pink"
col6 = "darkred"
colclear= "#1C00ff00"

resize <- function(g, fig_width=NA, fig_height=NA) {
  g_deparsed <- paste0(deparse(function() g), collapse = '')
  sub_chunk <- paste0("`","``{r sub_chunk_", floor(runif(1) * 10000), ", fig.height=", fig_height, ", fig.width=", fig_width, ", warning=FALSE, echo=FALSE}","\n(", g_deparsed, ")()","\n`","``")
  cat(knitr::knit(text = knitr::knit_expand(text = sub_chunk), quiet = TRUE))
}


Sport_mark_rate_finescale<-read_rds("Sport_mark_rate_finescale.RDS")

Sport_mark_rate_finescale_combined<-read_rds("Sport_mark_rate_finescale_combined.RDS")

models_combined<- read_rds("models_combined.RDS")

Season_south_no_nas<-read_rds("Season_south_no_nas.RDS")
Summer_south_no_nas<-read_rds("Summer_south_no_nas.RDS")
Season_north_aabm_no_nas<-read_rds("Season_north_aabm_no_nas.RDS")
Season_north_isbm_no_nas<-read_rds("Season_north_isbm_no_nas.RDS")
Season_cbc_isbm_no_nas<-read_rds("Season_cbc_isbm_no_nas.RDS")


Season_south_combined<-read_rds("Season_south_combined.RDS")
Summer_south_combined<-read_rds("Summer_south_combined.RDS")
Season_north_aabm_combined<-read_rds("Season_north_aabm_combined.RDS")
Season_north_isbm_combined<-read_rds("Season_north_isbm_combined.RDS")
Season_cbc_isbm_combined<-read_rds("Season_cbc_isbm_combined.RDS")


```

## Southern BC Spring and Fall fisheries

-   The best model was one with a gamma distribution
-   Next, we investigated if the fully interactive model is better than a subset of interactions. We used the dredge function from the MuMin package to sequentially drop terms (including all interactions).
-   The best model included summer creel, marked and kept status, finescale fishery, and season and various interactions of these terms
-   $$ catch = creel.summer+finescale.fishery+season+status+                                               creel.summer:finescale.fishery  + creel.summer:status+                                               finescale.fishery:season $$

```{r Modelling spring and fall subsetting, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

Spring_fall_model<-  glm(formula =catch_estimate + 3 ~ finescale_fishery_old + season +   status + creel_plus_summer:finescale_fishery_old + creel_plus_summer:status +  finescale_fishery_old:season + 1 + creel_plus_summer,  family=Gamma(link = "log"), data = Season_south_no_nas)


res_gam <- simulateResiduals(Spring_fall_model, plot = T, quantreg=T)

```

```{r Modelling all spring and fall southern BC fisheries, message=FALSE, warning=FALSE, results='hold'}

#### Adding confidence intervals based on model to a dataframe for plotting purposes
#based on this blog: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/

family.set <- family(Spring_fall_model)
ilink.family.set<- family.set$linkinv

mod<-Spring_fall_model

ndata<-Season_south_no_nas %>% group_by(status, finescale_fishery_old, finescale_fishery, season) %>%  tidyr::expand(creel_plus_summer = seq(0, max(creel_plus_summer), length=100))
  

## add the fitted values by predicting from the model for the new data
ndata<- add_column(ndata, fit = predict(mod, newdata = ndata, type = 'response'))
ndata<- bind_cols(ndata, setNames(as_tibble(predict(mod, ndata, se.fit = TRUE)[1:2]),
                                                   c('fit_link','se_link')))

ndata <- mutate(ndata,
                fit_resp  = ilink.family.set(fit_link),
                right_upr = ilink.family.set(fit_link + (2 * se_link)),
                right_lwr = ilink.family.set(fit_link - (2 * se_link)))
```

```{r summarizing spring and fall}
yearMonth2_season <- plyr::ddply(Sport_mark_rate_finescale, c( "YEAR", "MONTH", "finescale_fishery", "season"), summarise,
                         sum_creel = sum(creel, na.rm = TRUE), sum= sum(creel_plus, na.rm = TRUE), sum_historic= sum(historic_plus, na.rm = TRUE), sum_catch_estimate = sum(catch_estimate, na.rm = TRUE), sum_irec = sum(irec_calibrated, na.rm = TRUE)) %>% filter(finescale_fishery!="NA") %>% mutate(across(where(is.numeric), ~na_if(., 0))) 


yearMonth_catch_estimate_2_season<-yearMonth2_season %>% filter(sum_catch_estimate!=sum,sum_catch_estimate!=sum_historic, sum_catch_estimate!=sum_irec)

yearMonth_irec_2_season<-yearMonth2_season %>% filter(sum_catch_estimate==sum_irec)


```

```{r forloop seasonal spring and fall, results='asis', echo=FALSE}

yearMonth2_season_south<- yearMonth2_season %>% filter(!str_detect(finescale_fishery, "CBC|NBC")) %>%
  filter(season %in% c("spring", "fall"))
fishery_name_south<- sort(unique(yearMonth2_season_south$finescale_fishery))

  
for (i in 1:length(fishery_name_south)){
 
  cat("\n\n")
  cat("### ", paste0("", fishery_name_south[fishery_name_south== fishery_name_south[i]], " "),"\n\n") 
  
p1<-ggplot()+
  geom_tile(data=yearMonth2_season_south %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_y_discrete(limits=rev)+
  geom_tile(data=yearMonth2_season_south  %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear)+
  labs(title = paste("Coverage for", fishery_name_south[i]),
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013) 

p2<-ggplot()+
  geom_tile(data=yearMonth2_season_south %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  scale_y_discrete(limits=rev)+
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  geom_tile(data=yearMonth2_season_south%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  new_scale_fill() +
  geom_tile(data=yearMonth_catch_estimate_2_season%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col3, high = col4, na.value = colclear)+
  guides(fill=guide_legend(title="creel plus iREC estimates")) +
  new_scale_fill() +
  geom_tile(data=yearMonth_irec_2_season%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col5, high = col6, na.value = colclear)+
  guides(fill=guide_legend(title="iREC estimates")) +
  labs(
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013)


p<-p1+p2 + plot_layout(guides = "collect") & theme(legend.position = 'none')

cat("\n\n")
resize(p, 5, 2)


#####

dataminmax_marked_kept<- Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total")


g1<-ggplot(Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$creel_plus_summer)))

g2<-ggplot(Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
 scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$creel_plus_summer)))

g3<-ggplot(Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
  coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$creel_plus_summer)))

g4<-ggplot(Season_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
    coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$creel_plus_summer)))

g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
g
cat("\n\n")
 resize(g, 7, 5)
 
 
 m<-ggplot(Season_south_combined %>% filter(finescale_fishery==fishery_name_south[i])) +
    geom_point(size=2.5,  aes(y=creel_unfiltered_plus, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=creel_unfiltered_plus, x=YEAR,col=status, linetype = " Unfiltered creel and logbook"))+
    scale_shape_manual(values=c(1,1))+
    new_scale("shape")+
    scale_colour_viridis_d()+
    geom_point(size=2.5, aes(y=catch_estimate_predicted, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=catch_estimate_predicted, x=YEAR,col=status, linetype = "iREC included"))+
    scale_shape_manual(values=c(16,17))+
    scale_linetype_manual(values=c(2,1))+
    facet_wrap(~status, scales="free") + ggtitle(paste(fishery_name_south[i])) + theme_bw()
 
 
cat("\n\n") 
resize(m, 7, 5)
 cat("\n\n\n")
}

```

```{r plot spring fall together, results='asis', echo=FALSE, eval=FALSE}
# 
# dataminmax_marked_kept<- Season_south_no_nas %>% filter(status=="marked_Kept_total")
# dataminmax_marked_released<- Season_south_no_nas %>% filter(status=="marked_Released_total")
# dataminmax_unmarked_kept<- Season_south_no_nas %>% filter(status=="unmarked_Kept_total")
# dataminmax_unmarked_released<- Season_south_no_nas %>% filter(status=="unmarked_Released_total")
# 
# 
# g1<-ggplot(Season_south_no_nas %>% filter(season=="spring", status=="marked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
#   geom_point()+
#   #geom_line(ndata %>% filter(season=="spring", status=="marked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
#   geom_ribbon(ndata %>% filter(season=="spring", status=="marked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
#    theme_bw() +
#   scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
#   coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$creel_plus_summer)))
# 
# g2<-ggplot(Season_south_no_nas %>% filter(season=="spring", status=="marked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
#   geom_point()+
#   geom_line(ndata %>% filter(season=="spring", status=="marked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
#   geom_ribbon(ndata %>% filter(season=="spring", status=="marked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
#   theme_bw() +
#  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
#   coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$creel_plus_summer)))
# 
# g3<-ggplot(Season_south_no_nas %>% filter(season=="spring", status=="unmarked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
#   geom_point()+
#   geom_line(ndata %>% filter(season=="spring", status=="unmarked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
#   geom_ribbon(ndata %>% filter(season=="spring", status=="unmarked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
#   theme_bw() +
#   scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
#   coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$creel_plus_summer)))
# 
# g4<-ggplot(Season_south_no_nas %>% filter(season=="spring", status=="unmarked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
#   geom_point()+
#   geom_line(ndata %>% filter(season=="spring", status=="unmarked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
#   geom_ribbon(ndata %>% filter(season=="spring", status=="unmarked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
#    theme_bw() +
#   scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
#     coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$creel_plus_summer)))
# 
# g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
# g
# cat("\n\n\n")
#  resize(g, 7, 5)
```

## Southern BC Summer fisheries

-   The best model was one with a gamma distribution
-   Next, we investigated if the fully interactive model is better than a subset of interactions. We used the dredge function from the MuMin package to sequentially drop terms (including all interactions).
-   The best model included summer creel, marked and kept status, finescale fishery, and various interactions of these terms
-   $$ catch = creel.summer+finescale.fishery+status+                                               creel.summer:finescale.fishery  + creel.summer:status                                               $$

```{r Modelling summer subsetting, message=FALSE, warning=FALSE, results='hide', echo=FALSE}


Summer_model<- glm(formula = catch_estimate + 3 ~ finescale_fishery_old + status +creel_plus_summer:status + finescale_fishery_old:status +  1 + creel_plus_summer,  family=Gamma(link = "log"), data = Summer_south_no_nas)

res_gam <- simulateResiduals(Summer_model, plot = T, quantreg=T)

```

```{r Modelling all summer southern BC fisheries, message=FALSE, warning=FALSE, results='hold'}

#### Adding confidence intervals based on model to a dataframe for plotting purposes
#based on this blog: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/

family.set <- family(Summer_model)
ilink.family.set<- family.set$linkinv

mod<-Summer_model

ndata<-Summer_south_no_nas %>% group_by(status, finescale_fishery_old, finescale_fishery, season) %>%  tidyr::expand(creel_plus_summer = seq(0, max(creel_plus_summer), length=100))
  

## add the fitted values by predicting from the model for the new data
ndata<- add_column(ndata, fit = predict(mod, newdata = ndata, type = 'response'))
ndata<- bind_cols(ndata, setNames(as_tibble(predict(mod, ndata, se.fit = TRUE)[1:2]),
                                                   c('fit_link','se_link')))

ndata <- mutate(ndata,
                fit_resp  = ilink.family.set(fit_link),
                right_upr = ilink.family.set(fit_link + (2 * se_link)),
                right_lwr = ilink.family.set(fit_link - (2 * se_link)))

```

```{r forloop summer, results='asis', echo=FALSE}

yearMonth2_season_south<- yearMonth2_season %>% filter(!str_detect(finescale_fishery, "CBC|NBC")) %>%
  filter(season %in% c("summer"))
fishery_name_south<- sort(unique(yearMonth2_season_south$finescale_fishery))

  
for (i in 1:length(fishery_name_south)){
 
  cat("\n\n")
  cat("### ", paste0("", fishery_name_south[fishery_name_south== fishery_name_south[i]], " "),"\n\n") 
  
p1<-ggplot()+
  geom_tile(data=yearMonth2_season_south %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_y_discrete(limits=rev)+
  geom_tile(data=yearMonth2_season_south  %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear)+
  labs(title = paste("Coverage for", fishery_name_south[i]),
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013) 

p2<-ggplot()+
  geom_tile(data=yearMonth2_season_south %>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  scale_y_discrete(limits=rev)+
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  geom_tile(data=yearMonth2_season_south%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  new_scale_fill() +
  geom_tile(data=yearMonth_catch_estimate_2_season%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col3, high = col4, na.value = colclear)+
  guides(fill=guide_legend(title="creel plus iREC estimates")) +
  new_scale_fill() +
  geom_tile(data=yearMonth_irec_2_season%>% filter(finescale_fishery==fishery_name_south[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col5, high = col6, na.value = colclear)+
  guides(fill=guide_legend(title="iREC estimates")) +
  labs(
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013)


p<-p1+p2 + plot_layout(guides = "collect") & theme(legend.position = 'none')

cat("\n\n")
resize(p, 5, 2)


#####

dataminmax_marked_kept<- Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total")
dataminmax_marked_released<- Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total")


g1<-ggplot(Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$creel_plus_summer)))

g2<-ggplot(Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="marked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
 scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$creel_plus_summer)))

g3<-ggplot(Summer_south_no_nas %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Kept_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
  coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$creel_plus_summer)))

g4<-ggplot(Summer_south_no_nas%>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), aes(x=creel_plus_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), mapping=aes(y= fit, x=creel_plus_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_south[i], status=="unmarked_Released_total"), mapping=aes(y= fit,x=creel_plus_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
    coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$creel_plus_summer)))

g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
g
cat("\n\n")
 resize(g, 7, 5)
 
 
 m<-ggplot(Summer_south_combined %>% filter(finescale_fishery==fishery_name_south[i])) +
    geom_point(size=2.5,  aes(y=creel_unfiltered_plus, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=creel_unfiltered_plus, x=YEAR,col=status, linetype = " Unfiltered creel and logbook"))+
    scale_shape_manual(values=c(1,1))+
    new_scale("shape")+
    scale_colour_viridis_d()+
    geom_point(size=2.5, aes(y=catch_estimate_predicted, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=catch_estimate_predicted, x=YEAR,col=status, linetype = "iREC included"))+
    scale_shape_manual(values=c(16,17))+
    scale_linetype_manual(values=c(2,1))+
    facet_wrap(~status, scales="free") + ggtitle(paste(fishery_name_south[i])) + theme_bw()
 
 
cat("\n\n") 
resize(m, 7, 5)
 cat("\n\n\n")
}
```

## NBC AABM fisheries

-   The best model was one with a gamma distribution
-   Next, we investigated if the fully interactive model is better than a subset of interactions. We used the dredge function from the MuMin package to sequentially drop terms (including all interactions).
-   The best model included summer creel, marked and kept status, and season and various interactions of these terms
-   $$ catch = creel.summer+season+status + creel.summer:season $$

```{r Modelling NBC AABM subsetting, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

North_aabm_model<- glm(formula = catch_estimate + 1 ~ season + status + historic_summer:season +1 + historic_summer,  family=Gamma(link = "log"), data = Season_north_aabm_no_nas)

res_gam_drop_kept_spec <- simulateResiduals(North_aabm_model, plot = T, quantreg=T)

#summary(North_aabm_model_full_gamma_spec)

```

```{r Modelling NBC AABM, message=FALSE, warning=FALSE, results='hold'}


#### Adding confidence intervals based on model to a dataframe for plotting purposes
#based on this blog: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/

family.set <- family(North_aabm_model)
ilink.family.set<- family.set$linkinv

mod<-North_aabm_model

ndata<-Season_north_aabm_no_nas %>% group_by(status, finescale_fishery_old, finescale_fishery, season) %>%  tidyr::expand(historic_summer = seq(0, max(historic_summer), length=100))


## add the fitted values by predicting from the model for the new data
ndata<- add_column(ndata, fit = predict(mod, newdata = ndata, type = 'response'))
ndata<- bind_cols(ndata, setNames(as_tibble(predict(mod, ndata, se.fit = TRUE)[1:2]),
                                                   c('fit_link','se_link')))

ndata <- mutate(ndata,
                fit_resp  = ilink.family.set(fit_link),
                right_upr = ilink.family.set(fit_link + (2 * se_link)),
                right_lwr = ilink.family.set(fit_link - (2 * se_link)))

```

```{r forloop seasonal NBC AABM, results='asis', echo=FALSE}

yearMonth2_season_north_aabm<- yearMonth2_season %>% filter(str_detect(finescale_fishery, "NBC AABM"))
fishery_name_north_aabm<- sort(unique(yearMonth2_season_north_aabm$finescale_fishery))

  
for (i in 1:length(fishery_name_north_aabm)){
 
  cat("\n\n")
  cat("### ", paste0("", fishery_name_north_aabm[fishery_name_north_aabm== fishery_name_north_aabm[i]], " "),"\n\n") 
  
p1<-ggplot()+
  geom_tile(data=yearMonth2_season_north_aabm %>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_y_discrete(limits=rev)+
  geom_tile(data=yearMonth2_season_north_aabm  %>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear)+
  labs(title = paste("Coverage for", fishery_name_north_aabm[i]),
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013) 

p2<-ggplot()+
  geom_tile(data=yearMonth2_season_north_aabm %>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  scale_y_discrete(limits=rev)+
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  geom_tile(data=yearMonth2_season_north_aabm%>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  new_scale_fill() +
  geom_tile(data=yearMonth_catch_estimate_2_season%>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col3, high = col4, na.value = colclear)+
  guides(fill=guide_legend(title="creel plus iREC estimates")) +
  new_scale_fill() +
  geom_tile(data=yearMonth_irec_2_season%>% filter(finescale_fishery==fishery_name_north_aabm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col5, high = col6, na.value = colclear)+
  guides(fill=guide_legend(title="iREC estimates")) +
  labs(
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013)


p<-p1+p2 + plot_layout(guides = "collect") & theme(legend.position = 'none')

cat("\n\n")
resize(p, 5, 2)


#####
 
dataminmax_marked_kept<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Released_total")

dataminmax_marked_kept<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Released_total")

g1<-ggplot(Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$historic_summer)))

g2<-ggplot(Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="marked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
 scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$historic_summer)))

g3<-ggplot(Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
  coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$historic_summer)))

g4<-ggplot(Season_north_aabm_no_nas %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_aabm[i], status=="unmarked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
    coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$historic_summer)))

g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
g
cat("\n\n")
 resize(g, 7, 5) 
 
 
 
 
 m<-ggplot(Season_north_aabm_combined %>% filter(finescale_fishery==fishery_name_north_aabm[i])) +
    geom_point(size=2.5,  aes(y=historic, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=historic, x=YEAR,col=status, linetype = "Unfiltered creel and logbook"))+ 
    scale_shape_manual(values=c(1,1))+
    new_scale("shape")+
    scale_colour_viridis_d()+
    geom_point(size=2.5, aes(y=catch_estimate_predicted, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=catch_estimate_predicted, x=YEAR,col=status, linetype = "iREC included"))+ 
    scale_shape_manual(values=c(16,17))+
    scale_linetype_manual(values=c(1,2))+
    facet_wrap(~status, scales="free") + ggtitle(paste(fishery_name_north_aabm[i])) + theme_bw()
 
cat("\n\n") 
resize(m, 7, 4)
 cat("\n\n\n")
}

```

## NBC ISBM fisheries

-   The best model was one with a gamma distribution
-   Next, we investigated if the fully interactive model is better than a subset of interactions. We used the dredge function from the MuMin package to sequentially drop terms (including all interactions).
-   The best model included summer creel, marked and kept status, and season and various interactions of these terms

```{=html}
<!-- -->
```
-   $$ catch = creel.summer+season+status + season:status                                         $$

```{r Modelling NBC ISBM subsetting, message=FALSE, warning=FALSE, results='hide', echo=FALSE}

North_isbm_model<- glm(formula = catch_estimate + 1 ~ season + status + status:season + 1 + historic_summer,  family=Gamma(link = "log"), data = Season_north_isbm_no_nas)

res_gam_drop_kept_spec <- simulateResiduals(North_isbm_model, plot = T, quantreg=T)

```

```{r Modelling NBC ISBM, message=FALSE, warning=FALSE, results='hold'}

#### Adding confidence intervals based on model to a dataframe for plotting purposes
#based on this blog: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/

family.set <- family(North_isbm_model)
ilink.family.set<- family.set$linkinv

mod<-North_isbm_model

ndata<-Season_north_isbm_no_nas %>% group_by(status, finescale_fishery_old, finescale_fishery, season) %>%  tidyr::expand(historic_summer = seq(0, max(historic_summer), length=100))

## add the fitted values by predicting from the model for the new data
ndata<- add_column(ndata, fit = predict(mod, newdata = ndata, type = 'response'))
ndata<- bind_cols(ndata, setNames(as_tibble(predict(mod, ndata, se.fit = TRUE)[1:2]),
                                                   c('fit_link','se_link')))

ndata <- mutate(ndata,
                fit_resp  = ilink.family.set(fit_link),
                right_upr = ilink.family.set(fit_link + (2 * se_link)),
                right_lwr = ilink.family.set(fit_link - (2 * se_link)))
```

```{r forloop seasonal NBC ISBM, results='asis', echo=FALSE}

yearMonth2_season_north_isbm<- yearMonth2_season %>% filter(str_detect(finescale_fishery, "NBC ISBM"))
fishery_name_north_isbm<- sort(unique(yearMonth2_season_north_isbm$finescale_fishery))

  
for (i in 1:length(fishery_name_north_isbm)){
 
  cat("\n\n")
  cat("### ", paste0("", fishery_name_north_isbm[fishery_name_north_isbm== fishery_name_north_isbm[i]], " "),"\n\n") 
  
p1<-ggplot()+
  geom_tile(data=yearMonth2_season_north_isbm %>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_y_discrete(limits=rev)+
  geom_tile(data=yearMonth2_season_north_isbm  %>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear)+
  labs(title = paste("Coverage for", fishery_name_north_isbm[i]),
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013) 

p2<-ggplot()+
  geom_tile(data=yearMonth2_season_north_isbm %>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  scale_y_discrete(limits=rev)+
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  geom_tile(data=yearMonth2_season_north_isbm %>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  new_scale_fill() +
  geom_tile(data=yearMonth_catch_estimate_2_season%>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col3, high = col4, na.value = colclear)+
  guides(fill=guide_legend(title="creel plus iREC estimates")) +
  new_scale_fill() +
  geom_tile(data=yearMonth_irec_2_season%>% filter(finescale_fishery==fishery_name_north_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col5, high = col6, na.value = colclear)+
  guides(fill=guide_legend(title="iREC estimates")) +
  labs(
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013)


p<-p1+p2 + plot_layout(guides = "collect") & theme(legend.position = 'none')

cat("\n\n")
resize(p, 5, 2)


#####
 
dataminmax_marked_kept<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Released_total")

dataminmax_marked_kept<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Released_total")

g1<-ggplot(Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$historic_summer)))

g2<-ggplot(Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="marked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
 scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$historic_summer)))

g3<-ggplot(Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
  coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$historic_summer)))

g4<-ggplot(Season_north_isbm_no_nas %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_north_isbm[i], status=="unmarked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
    coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$historic_summer)))

g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
g
cat("\n\n")
 resize(g, 7, 5) 
 
 
 
 
 m<-ggplot(Season_north_isbm_combined %>% filter(finescale_fishery==fishery_name_north_isbm[i])) +
    geom_point(size=2.5,  aes(y=historic, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=historic, x=YEAR,col=status, linetype = "Unfiltered creel and logbook"))+ 
    scale_shape_manual(values=c(1,1))+
    new_scale("shape")+
    scale_colour_viridis_d()+
    geom_point(size=2.5, aes(y=catch_estimate_predicted, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=catch_estimate_predicted, x=YEAR,col=status, linetype = "iREC included"))+ 
    scale_shape_manual(values=c(16,17))+
    scale_linetype_manual(values=c(1,2))+
    facet_wrap(~status, scales="free") + ggtitle(paste(fishery_name_north_isbm[i])) + theme_bw()
 
cat("\n\n") 
resize(m, 7, 4)
 cat("\n\n\n")
}

```

## CBC ISBM fisheries

-   The best model was one with a gamma distribution
-   Next, we investigated if the fully interactive model is better than a subset of interactions. We used the dredge function from the MuMin package to sequentially drop terms (including all interactions).
-   The best model included summer creel, marked and kept status, and season and various interactions of these terms

```{=html}
<!-- -->
```
-   $$ catch = creel.summer+status                                      $$

```{r Modelling CBC ISBM subsetting, message=FALSE, warning=FALSE, results='hide', echo=FALSE}


#Chosen model:
cbc_isbm_model<- glm(formula = catch_estimate + 1 ~  status + 1 + historic_summer,  family=Gamma(link = "log"), data = Season_cbc_isbm_no_nas)
res_gam_drop_kept_spec <- simulateResiduals(cbc_isbm_model, plot = T, quantreg=T)

```

```{r Modelling CBC ISBM, message=FALSE, warning=FALSE, results='hold'}

#### Adding confidence intervals based on model to a dataframe for plotting purposes
#based on this blog: https://fromthebottomoftheheap.net/2018/12/10/confidence-intervals-for-glms/

family.set <- family(cbc_isbm_model)
ilink.family.set<- family.set$linkinv

mod<-cbc_isbm_model

ndata<-Season_cbc_isbm_no_nas %>% group_by(status, finescale_fishery_old, finescale_fishery, season) %>%  tidyr::expand(historic_summer = seq(0, max(historic_summer), length=100))

## add the fitted values by predicting from the model for the new data
ndata<- add_column(ndata, fit = predict(mod, newdata = ndata, type = 'response'))
ndata<- bind_cols(ndata, setNames(as_tibble(predict(mod, ndata, se.fit = TRUE)[1:2]),
                                                   c('fit_link','se_link')))

ndata <- mutate(ndata,
                fit_resp  = ilink.family.set(fit_link),
                right_upr = ilink.family.set(fit_link + (2 * se_link)),
                right_lwr = ilink.family.set(fit_link - (2 * se_link)))
```

```{r forloop seasonal CBC ISBM, results='asis', echo=FALSE}

yearMonth2_season_cbc_isbm<- yearMonth2_season %>% filter(str_detect(finescale_fishery, "CBC S"))
fishery_name_cbc_isbm<- sort(unique(yearMonth2_season_cbc_isbm$finescale_fishery))

  
for (i in 1:length(fishery_name_cbc_isbm)){
 
  cat("\n\n")
  cat("### ", paste0("", fishery_name_cbc_isbm[fishery_name_cbc_isbm== fishery_name_cbc_isbm[i]], " "),"\n\n") 
  
p1<-ggplot()+
  geom_tile(data=yearMonth2_season_cbc_isbm %>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_y_discrete(limits=rev)+
  geom_tile(data=yearMonth2_season_cbc_isbm  %>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear)+
  labs(title = paste("Coverage for", fishery_name_cbc_isbm[i]),
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013) 

p2<-ggplot()+
  geom_tile(data=yearMonth2_season_cbc_isbm %>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  scale_y_discrete(limits=rev)+
  guides(fill=guide_legend(title="creel and logbook estimates")) +
  geom_tile(data=yearMonth2_season_cbc_isbm %>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_historic),colour = "white") +
  scale_fill_gradient(low = col1, high = col2, na.value = colclear) +
  new_scale_fill() +
  geom_tile(data=yearMonth_catch_estimate_2_season%>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col3, high = col4, na.value = colclear)+
  guides(fill=guide_legend(title="creel plus iREC estimates")) +
  new_scale_fill() +
  geom_tile(data=yearMonth_irec_2_season%>% filter(finescale_fishery==fishery_name_cbc_isbm[i]), aes(x=YEAR, y=as.factor(MONTH), fill = sum_catch_estimate),colour = "white") +
  scale_fill_gradient(low = col5, high = col6, na.value = colclear)+
  guides(fill=guide_legend(title="iREC estimates")) +
  labs(
       x = "Year", y = "Month") +
  theme_bw() + theme_minimal() + geom_vline(xintercept = 2013)


p<-p1+p2 + plot_layout(guides = "collect") & theme(legend.position = 'none')

cat("\n\n")
resize(p, 5, 2)


#####
 
dataminmax_marked_kept<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Released_total")

dataminmax_marked_kept<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Kept_total")
dataminmax_marked_released<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Released_total")
dataminmax_unmarked_kept<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Kept_total")
dataminmax_unmarked_released<- Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Released_total")

g1<-ggplot(Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#440154"))+  scale_fill_manual(values=c("#440154"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_kept$catch_estimate)), xlim = c(0,max(dataminmax_marked_kept$historic_summer)))

g2<-ggplot(Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="marked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
 scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#31688e"))+  scale_fill_manual(values=c("#31688e"))+
  coord_cartesian(ylim = c(0,max(dataminmax_marked_released$catch_estimate)), xlim = c(0,max(dataminmax_marked_released$historic_summer)))

g3<-ggplot(Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Kept_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Kept_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status), alpha = 0.10)+
  theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#35b779"))+  scale_fill_manual(values=c("#35b779"))+
  coord_cartesian(ylim = c(0,max(dataminmax_unmarked_kept$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_kept$historic_summer)))

g4<-ggplot(Season_cbc_isbm_no_nas %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Released_total"), aes(x=historic_summer,  y= catch_estimate, col=status))+
  geom_point()+
  geom_line(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Released_total"), mapping=aes(y= fit, x=historic_summer, col=status))+
  geom_ribbon(ndata %>% filter(finescale_fishery==fishery_name_cbc_isbm[i], status=="unmarked_Released_total"), mapping=aes(y= fit,x=historic_summer, ymin = right_lwr, ymax = right_upr, fill=status, col=status), alpha = 0.10)+
   theme_bw() +
  scale_size_continuous(range=c(1,3))+ scale_colour_manual(values=c("#fde725"))+  scale_fill_manual(values=c("#fde725"))+
    coord_cartesian(ylim = c(0,max(dataminmax_unmarked_released$catch_estimate)), xlim = c(0,max(dataminmax_unmarked_released$historic_summer)))

g<-g1+g2 + g3+g4 + plot_layout(guides = "collect") 
g
cat("\n\n")
 resize(g, 7, 5) 
 
 
 
 
 m<-ggplot(Season_cbc_isbm_combined %>% filter(finescale_fishery==fishery_name_cbc_isbm[i])) +
    geom_point(size=2.5,  aes(y=historic, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=historic, x=YEAR,col=status, linetype = "Unfiltered creel and logbook"))+ 
    scale_shape_manual(values=c(1,1))+
    new_scale("shape")+
    scale_colour_viridis_d()+
    geom_point(size=2.5, aes(y=catch_estimate_predicted, x=YEAR,col=status, fill=status, shape=pred_cat))+
    geom_line(aes(y=catch_estimate_predicted, x=YEAR,col=status, linetype = "iREC included"))+ 
    scale_shape_manual(values=c(16,17))+
    scale_linetype_manual(values=c(1,2))+
    facet_wrap(~status, scales="free") + ggtitle(paste(fishery_name_cbc_isbm[i])) + theme_bw()
 
cat("\n\n") 
resize(m, 7, 4)
 cat("\n\n\n")
}

```
